Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on results

This section discusses a selection of bugs reports. The selection
criteria we used was: (i) to cover each of the engines we were able to
find bugs--\chakra, \jsc, and \veight, (ii) to cover a different
successful technique--test transplantation and differential testing
(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
rejected bug report, and (iv) the test is short.

%% \CodeIn{\{var a =
%%   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
%%   assert(+a === 0)\}}

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\Fix{XX}.} The code
snippet below shows the test input we used to reveal a bug in
\chakra.

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
{var a =
  {valueOf:~function(){ return "\x00"}}
  assert(+a === 0)}
  \end{lstlisting}
  \normalsize
  %% \caption{Warning captured as \hi{} priority.}
  %% \label{fig:hi-priority}
\end{figure}

The object property \CodeIn{valueOf} stores a function
that returns a primitive value identifying the target
object~\cite{valueof}. The original version of this code returns an
empty string whereas the version of the code modified by the \radamsa{}
fuzzer~\cite{radamsa} returns a string representation of a null
character (\CodeIn{NUL} in ascii). The unary plus expression
``\CodeIn{+a}", used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} \Igor{
  \chakra{} converte incorretamente o valor hexadecimal para
  0 e a expressao +0 resulta em 0, o que faz com que o teste passe. Os outros
  engines consideram o hexadecimal invalido (valor esperado), 
  quando o hexadecimal nao pode ser convertido, espera-se que retorne NaN, que +NaN resulta em NaN.
  }evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

@@

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assert, assertEq, var, yield, in, function, eval,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
eval(function b (a) {
  break;
});
  \end{lstlisting}
  \normalsize
  %% \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
  %% and reported in \veight{} engine}
\end{figure}

This code snippet was obtained by fuzzing a Test262 test with
\quickfuzz. In its original version, a string (omitted for space),
passed as argument to the \CodeIn{eval} function, encoded the actual
test. The fuzzer replaced the string argument with a function whose
body is a \CodeIn{break} statement outside a valid block
statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
how eval should be handle code containing a function declaration.
According to specification~\cite{break-statement}, the break statement
should throw an early error--in this case a SyntaxError--if the break
statement is not nested in an iterational or a switch statement. In
this case, all engines behave as expected but \veight{} pass without
failures.

%% \Igor{
%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
%%   function declaration. The fuzzer removes the function declaration and 
%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
%%   the break statement should throw an early error (in this case a SyntaxError) 
%%   if the break statement is not nested in an iterational or a switch statement. All engines works
%%   as expected but \veight{} pass without failures.
%% }

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
code snippet below shows an example input related to a bug report that
we issued to the \chakra\ development team, but they did not accept.

@@

This is a testcase original from the \jsc{} suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, but this test uses a long integer
instead. As result, the engine crashes. The team answered that this
was an incompatibility by design as the function was not expected to
receive such a long value.

\subsection{Threats To Validity}

>>>>

This section discusses a selection of bugs reports. The selection
criteria we used was: (i) to cover each of the engines we were able to
find bugs--\chakra, \jsc, and \veight, (ii) to cover a different
successful technique--test transplantation and differential testing
(with \radamsa\ and with \quickfuzz), and (iii) to cover a case of
rejected bug report.

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:cross-testing}.} 
The JS code \CodeIn{\{var a =
  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the Radamsa fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} \Igor{
  \chakra{} converte incorretamente o valor hexadecimal para
  0 e a expressao +0 resulta em 0, o que faz com que o teste passe. Os outros
  engines consideram o hexadecimal invalido (valor esperado), 
  quando o hexadecimal nao pode ser convertido, espera-se que retorne NaN, que +NaN resulta em NaN.
  }evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

@@

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assert, assertEq, var, yield, in, function, eval,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
// Original file
eval(
"{ 
    function f() { 
      return 'declaration'; 
    } 
 }
 assert.sameValue(typeof f, 'function');
 \assert.sameValue(f(), 'declaration');"
);
------------------------------------------
// Fuzzed file
eval(function b (a) {
  break;
});
  \end{lstlisting}
  \normalsize
  \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
  and reported in \veight{} engine}
\end{figure}

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
code snippet below shows an example input related to a bug report that
we issued to the \chakra\ development team, but they did not accept.
This is a testcase original from the \jsc{} suite that the
\radamsa\ fuzzer modified. Instead of the long integer passed as
argument to \CodeIn{"foo".repeat()}, the original test used the
integer literal 3. The engine crashes on this input as result. The
team answered that this was an incompatibility by design as the
function repeat was not expected to receive such a long value.

@@

\subsection{Threats}
